---
title: "COMPANY NAME - EXPLORATORY DATA ANALYSIS"
author: "Prepared by: CBRE Business Analytics"
date: '`r paste("Date:",Sys.Date())`'
output:
  pdf_document: 
    latex_engine: xelatex
header-includes:
- \usepackage{titling}
- \usepackage{fancyhdr}
- \pretitle{\begin{center} \includegraphics[width=4in,height=2in]{CBRE_Group_logo.svg.png}\Huge\\
  \end{center}\begin{center}\LARGE}
- \pagestyle{fancy}
- \fancyhead[L]{\includegraphics[width=1in,height=0.5in]{CBRE_Group_logo.svg.png}\LARGE\\}
- \fancyhead[R]{}
- \renewcommand{\headrulewidth}{0.7mm}
- \renewcommand{\footrulewidth}{0.35mm}
- \posttitle{\end{center}}
- \usepackage{fontspec}
- \setmainfont{Futura Bk BT}
- \usepackage{caption}
- \captionsetup[figure]{labelformat=empty}
- \usepackage{xcolor}
- \usepackage{sectsty}
- \definecolor{energizinggreen}{RGB}{191,216,87}
- \allsectionsfont{\color{energizinggreen}}
- \setlength{\headheight}{50pt}
- \setlength{\footskip}{-50pt}
always_allow_html: yes
allow_html_dependencies: yes
urlcolor: blue
---

\newpage
\hypersetup{linkcolor=black}
\tableofcontents
\newpage

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(tinytex.verbose = TRUE)
options("scipen"=100, "digits"=4)
```

```{r libraries}
library(psych)
library(dplyr)
library(tidyr)
```

## 1. Heading 1

Description

## 2. Heading 2

+ Point 1
+ Point 2
  + Sub point 1
  + Sub Point 2
+ Point 2

## 3. Heading 3

### 3.1 Sub-Heading 1

Description

### 3.2 Sub-Heading 2

Description 

\newpage

## Support

In case of any question or support, please contact:

+ [Shane Trefftzs (Shane.Trefftzs@cbre.com)](mailto:Shane.Trefftzs@cbre.com)
+ [Dana Lindquist (Dana.Lindquist@cbre.com)](mailto:Dana.Lindquist@cbre.com)
+ [Inderpaul Singh (Inderpaul.Singh@cbre.com)](mailto:Inderpaul.Singh@cbre.com)
+ [Vishal Sharma (Vishal.Sharma1@cbre.com)](mailto:Vishal.Sharma1@cbre.com)
